TE_computation

### 2021-03-22 computational model/TE_computation_Simulation.Rmd
updated simulation analysis

# Read in data
```{r}
TE_computation <- read.csv(here::here("computational model/TE_computation.csv"))
```

@@

# Simulation 2
## Patterns of translation equivalent learning as a function of different developmental timepoints
### V = 150, 300, 450, or 600
```{r}
# V = 600
## Generating the parameters
V <- 600
W <- V # holding W constant
B <- seq(0.5, 1, by = 0.1) # a range of Balance, i.e. proportion use of dominant language (B ≤ .50)

@@

# V = 450
## Generating the parameters
V <- 450
W <- V # holding W constant
B <- seq(0.5, 1, by = 0.1) # a range of Balance, i.e. proportion use of dominant language (B ≤ .50)

@@

# V = 300
## Generating the parameters
V <- 300
W <- V # holding W constant
B <- seq(0.5, 1, by = 0.1) # a range of Balance, i.e. proportion use of dominant language (B ≤ .50)

@@

# V = 150
## Generating the parameters
V <- 150
W <- V # holding W constant
B <- seq(0.5, 1, by = 0.1) # a range of Balance, i.e. proportion use of dominant language (B ≤ .50)

@@

# Combining all the dataframes
data_Simulation2 <- rbind(TE_V150, TE_V300, TE_V450, TE_V600) %>%
  # Create other variables
  mutate(D = B*W, # Words produced in the dominant language
         N = (1-B)*W, # Words produced in non-dominant language
         TE = (D*N)/V, # If D and N are independent, TE = DN/V
         Du = D-TE, # Unique words in dominant language
         Nu = N-TE) %>% # Unique words in non-dominant language
  # Round to keep whole numbers only
  mutate_at(vars(-B), round, 0)

# Visualizing Simulation 2
Simulation2 <- data_Simulation2 %>%
  pivot_longer(-c(V, W, B), names_to = "vocab_type", values_to = "number") %>%
  filter(vocab_type %notin% c("D", "N")) %>%
  mutate(vocab_type = factor(vocab_type, levels=c("Nu", "Du", "TE"))) %>%
  group_by(V, B, vocab_type) %>%
  summarise(n_words = mean(number)) %>%
  ggplot(aes(x = B, y = n_words, fill = vocab_type)) + 
  geom_bar(position="stack", stat="identity") +
  facet_grid(. ~ V) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) + 
  #scale_y_continuous(limits = c(0, 1200)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90), 
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=12)) + 
  labs(x = "Balance", 
       y = "Number of concepts", 
       title = "Vocabulary composition across different developmental timepoints (V)")

>>>>

@@

# Simulation 2
## Patterns of translation equivalent learning as a function of different developmental timepoints
### V = 150, 300, 450, or 600
```{r}
# V = 600
## Generating the parameters
V <- 600
W <- V # holding W constant
B <- seq(0.5, 1, by = 0.01) # a range of Balance, i.e. proportion use of dominant language (B ≤ .50)

@@

# V = 450
## Generating the parameters
V <- 450
W <- V # holding W constant
B <- seq(0.5, 1, by = 0.01) # a range of Balance, i.e. proportion use of dominant language (B ≤ .50)

@@

# V = 300
## Generating the parameters
V <- 300
W <- V # holding W constant
B <- seq(0.5, 1, by = 0.01) # a range of Balance, i.e. proportion use of dominant language (B ≤ .50)

@@

# V = 150
## Generating the parameters
V <- 150
W <- V # holding W constant
B <- seq(0.5, 1, by = 0.01) # a range of Balance, i.e. proportion use of dominant language (B ≤ .50)

@@

# Combining all the dataframes
data_Simulation2 <- rbind(TE_V150, TE_V300, TE_V450, TE_V600) %>%
  # Create other variables
  mutate(D = B*W, # Words produced in the dominant language
         N = (1-B)*W, # Words produced in non-dominant language
         TE = (D*N)/V, # If D and N are independent, TE = DN/V
         DU = D-TE, # Unique words in dominant language
         NU = N-TE) %>% # Unique words in non-dominant language
  # Round to keep whole numbers only
  mutate_at(vars(-B), round, 0)

# Visualizing Simulation 2
Simulation2 <- data_Simulation2 %>%
  mutate(bin_B = case_when(B < 0.6 ~ "0.5",
                           B >= 0.6 & B < 0.7 ~ "0.6",
                           B >= 0.7 & B < 0.8 ~ "0.7",
                           B >= 0.8 & B < 0.9 ~ "0.8",
                           TRUE ~ "0.9")) %>%
  pivot_longer(-c(V, W, B, bin_B), names_to = "vocab_type", values_to = "number") %>%
  filter(vocab_type %notin% c("D", "N")) %>%
  mutate(vocab_type = factor(vocab_type, levels=c("NU", "DU", "TE"))) %>%
  group_by(V, bin_B, vocab_type) %>%
  summarise(n_words = mean(number)) %>%
  ggplot(aes(x = bin_B, y = n_words, fill = vocab_type)) + 
  geom_bar(position="stack", stat="identity") +
  facet_grid(. ~ V) +
  scale_fill_manual(values = c("#1f78b4", "#a6cee3", "#33a02c")) + 
  #scale_y_continuous(limits = c(0, 1200)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90), 
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=12)) + 
  labs(x = "Balance", 
       y = "Number of concepts", 
       title = "Vocabulary composition across different developmental timepoints (V)")
